%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Latex Resume
% Version 1.0
% 
% Author: Justin Espiritu
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\name{Justin L. Espiritu} % Name
\title{Software Engineer} % First Title
\title{Developer} % Second Title
\address{2381 Katy Ct Oshkosh, WI 54904} % Address
\phone{920-279-9796} % Phone number
\email{Espiritu.L.Justin@gmail.com} % Email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of Wisconsin - Oshkosh} \hfill {\em December 2018} \\
{\em Computer Science \seperator Software Engineering Emphasis} 

\end{rSection}

%-----------------------------------------------------------------------------------------------
%    Professional Experience
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Professional Experience}

    \begin{rSubsection}{Teamcenter Implementations Engineer}{January 2019 - Present}{Mercury Marine}{Fond Du Lac, WI}
        \item Collaborate with local and remote team members in developing and executing TEamcenter solutions
        \item Configure teamcenter BMIDE, BOM Management, Workflows, Access control, Change Management, Dispatcher Configuration, and other Teamcenter Modules
        \item Customize Teamcenter using standard Teamcenter API's
        \item Troubleshoot Teamcenter technical issues at various levels such as installation, deployment, and configuration
        \item Perform data modeling and data mapping process in assistance with business analysts \& solution architects
    \end{rSubsection}

    \begin{rSubsection}{Web Application Developer}{March 2017 - December 2018}{University of Wisconsin - Oshkosh}{Oshkosh, WI}
        \item Rewrote the Advising Worksheet, an application for advisors at the Under Graduate Advising Resource Center (UARC) and 
            Student Success Center (SSC) that streamlines the process of creating eduucation/graduation plans for students, from 
            plone to AngularJS. 
        \item Created AngularJS directive for developer to accelerate \& simplify the process to create multi-add fields to forms
        \item Provided detailed documentation in Confluence for developers to use newly created directives \& applications
    \end{rSubsection}

    % \begin{rSubsection}{Research Assistant}{Jan 2017 - May 2017}{University of Wisconsin - Oshkosh}{Oshkosh, WI}
    %     \item Created a program in Python 2 using the Natural Language Tool Kit (NLTK) library to gather data on articles and 
    %         create simple summaries on provided articles.
    % \end{rSubsection}

\end{rSection}
%----------------------------------------------------------------------------------------
%	Projects
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Modeling and Analysis \ & AutoCad, Revit, StaadPro \\
Software \& Tools & MS Office, Latex \\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

\begin{rSubsection}{SJ Contracts, Pune}{June 2016}{Site Engineer}{}
\item On-site internship under this leading construction company. Learned and implemented various aspects such as quantity estimation, labour management and safety precautions.
\end{rSubsection}


\end{rSection}


%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Academic Achievements} 
 Runners up in B.G.Shirke Vidyarthi Competition for Innovative Project organized by Pune Construction Engineering Research Foundation in January 2018
\item Won First Prize in Model Making Competition Organized by Symbiosis Institute of Technology, Pune.
\end{rSection}

\newpage

%----------------------------------------------------------------------------------------
% Extra Curricular
%----------------------------------------------------------------------------------------
\begin{rSection}{Extra-Cirrucular} \itemsep -3pt
\item Co-Organized “ Nirmitee 2017” - a National Symposium of Civil Department of MIT, Pune
\item Attended a workshop on Autodesk Revit at IIT Bombay in 2014.
\item Winner of Inter Departmental Football Competition 2015.
\item Member of the  Rotaract Club Of Pune Pride from 2014 to 2017.
\item Worked for a start-up company Named OUST as a Regional Marketing Manager
%\item Trained and disciplined in National Cadet Corps (NCC), IIT Kanpur for a year.
 %\item  Participated in Vijyoshi Camp 2012 organized at Indian Institute of Science, Bangalore.
 %\item Won 2nd position in Kho-Kho in Intramurals conducted by Physical Education Section, IIT Kanpur.
 %\item Pursued French as second language during secondary school from Grade 6 to Grade 10. Also participated in French Song Competition and French G.K. Quiz in Class 10th. %

\end{rSection}

\begin{rSection}{Personal Traits}
\item Highly motivated and eager to learn new things.
\item Strong motivational and leadership skills.
\item Ability to work as an individual as well as in group.
\end{rSection}
\end{document}